---
title: "Using GenderGuesser"
author: "Eamon Caddigan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

GenderGuesser uses the API at [genderize.io](https://genderize.io) to guess the gender of a name. Right now, GenderGuesser only exports a single function, `guessGender`. Calling this function returns a `data.frame` containing the results from [genderize.io](https://genderize.io).

```{r}
library("GenderGuesser")

# Call with a single name
guessGender("Natalie")

# Call with multiple names
guessGender(c("Liam", "Taidghin", "Eamon", "Sean"))
```

[genderize.io](https://genderize.io) can refine results based on language or country.

```{r}
# "Kim" is usually a female name in the US
guessGender("Kim", countryCode = "US")

# But "Kim" is usually a male name in Denmark (use the ISO 3166-1 alpha-2 country code)
guessGender("Kim", countryCode = "DK")

# You can use the ISO 639-1 language code instead
guessGender("Kim", languageCode = "da")
```

You can purchase an API key from [genderize.io](https://genderize.io) to get around their rate limit (100 names per day). Pass it to the function using the `apiKey` argument.
